---
title: "Prediction of MPG by Car Parameters"
author: "Miao"
date: "August 23, 2015"
output: slidy_presentation
---

## Development of Application

### Part1: Shiny Application  
- URL: *https://leemiao1984.shinyapps.io/carmpg*
- A shiny Application shows the relationship between variables and MPG.

### Part2: Reproducible Pitch Presentation  
- URL: *http://rpubs.com/leemiao1984/Developing_Data_Products_Project*

### Get all SourceCode @Github:

```
git clone https://github.com/leemiao1984/Developing_Data_Product
```

## mtcars dataset - Description

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.

```{r}
library(datasets)
head(mtcars, 3)
```

---

## mtcars dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Analysis - main code

```{r, eval=FALSE}
  ModelFit <- lm(mpg ~ hp + cyl + wt + am, data=mtcars)

  mpg <- function(hp, cyl, wt, am) {
    ModelFit$coefficients[1] + ModelFit$coefficients[2] * hp + 
      ModelFit$coefficients[3] * cyl + ModelFit$coefficients[4] * wt +     ModelFit$coefficients[5]* am
  }
  ...
  function(input, output) {
    adjusted_weight <- reactive({input$wt/1000})
    predicted_mpg <- reactive({mpg(input$hp, as.numeric(input$cyl), adjusted_weight(),as.numeric(input$am))})
    output$inputValues <- renderPrint({paste(input$cyl, "cylinders, ",
                                             input$hp, "horsepower, ",
                                             input$wt, "lbs, ",
                                             input$am, "transmission")})
    output$prediction <- renderPrint({paste(round(predicted_mpg(), 2), "miles per gallon")})
    output$plots <- renderPlot({
      par(mfrow = c(2, 2))
      # (1, 1)
      with(mtcars, plot(hp, mpg,
                        xlab='Gross Horsepower',
                        ylab='MPG',
                        main='MPG vs Horsepower'))
      points(input$hp, predicted_mpg(), col='red', cex=3)                 
      # (1, 2)
      with(mtcars, plot(cyl, mpg,
                        xlab='Number of Cylinders',
                        ylab='MPG',
                        main='MPG vs Cylinders'))
      points(as.numeric(input$cyl), predicted_mpg(), col='red', cex=3)  
      # (2, 1)
      with(mtcars, plot(wt, mpg,
                        xlab='Weight (lb/1000)',
                        ylab='MPG',
                        main='MPG vs Weight'))
      points(adjusted_weight(), predicted_mpg(), col='red', cex=3)
      # (2, 2)
      with(mtcars, plot(wt, am,
                        xlab='Transmission',
                        ylab='MPG',
                        main='MPG vs Transmission'))
      points(as.numeric(input$am), predicted_mpg(), col='red', cex=3)  
    })
  }
```
